---
title: "codeToRun"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{codeToRun}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 16,
  fig.height = 10,
  out.width = "100%",
  fig.align = "center"
)


```{r setup}
library(omoptrend)
library(Eunomia)
library(DatabaseConnector)
```

```{r}
# Get Eunomia connection ----------------------------------------------------------------------
connectionDetails <- Eunomia::getEunomiaConnectionDetails()

conn <- connect(connectionDetails)
```

```{r}
# Extract data  -------------------------------------------------------------------------------
df <- extractPatients(connection = conn, cdmSchema = "main")

# The top 10 records of the extracted data ----------------------------------------------------
head(df, 10)
```

```{r yearly-trend, fig.width=20, fig.height=20} 
# Plot trends by YEAR -------------------------------------------------------------------------
plotTrend(data = df, byMonth = FALSE)
```

```{r monthly-trend, fig.width=20, fig.height=20} 
# Plot trends by MONTH -------------------------------------------------------------------------
plotTrend(data = df, byMonth = TRUE)
```

```{r, eval=FALSE}
# Launch Shiny app (interactive, not run during vignette build) --------------------------------
launchShinyApp(df)
```

```{r, eval=FALSE}
# Launch Shiny app (interactive, not run during vignette build) --------------------------------
launchShinyAppDemo()
```